\documentclass[letterpaper,11pt]{article}
%Margin setup

\setlength{\voffset}{0.05in}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{10in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{10.5in}
\setlength{\topmargin}{-0.25in}
\setlength{\textwidth}{8in}
\setlength{\topskip}{0in}
\setlength{\evensidemargin}{-0.25in}
\setlength{\oddsidemargin}{-0.75in}
\usepackage{shading}
\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-6pt}}
\newcommand{\resitemdescription}[2]{\item \textbf{#1} #2 \vspace{-6pt}}
\newcommand{\resheading}[1]{{\large \parashade[.9]{sharpcorners}{\textbf{#1}}}\vspace{-20pt}}
\newcommand{\objectiveresheading}[1]{{\parashade[.9]{sharpcorners}{\textbf{\Large{Objective: }\large{#1}}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2
\end{tabular*}
\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
		\textit{#3} & \textit{#4}
\end{tabular*}\vspace{-8pt}}

\newcommand{\ressubheadingoneline}[2]{
\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
\end{tabular*}\vspace{-8pt}}
% Constants
% Me
\newcommand{\myname}[0]{Jason R. Berlinsky}
\newcommand{\myphone}[0]{973-933-1487}
\newcommand{\myemail}[0]{jason@jasonberlinsky.com}
\newcommand{\myaddress}[0]{8 Craig Road}
\newcommand{\mycity}[0]{Morristown}
\newcommand{\mystate}[0]{NJ}
\newcommand{\myzip}[0]{07960}
\newcommand{\myurl}[0]{http://www.jasonberlinsky.com}

% Company
\newcommand{\recipient}[0]{Mrs. Sandee Weiner}
\newcommand{\recipienttitle}[0]{Vice President of Collaboration \& Social Media}
\newcommand{\company}[0]{Bank of America}
\newcommand{\companyaddress}[0]{PO Box 79}
\newcommand{\companycity}[0]{Wayne}
\newcommand{\companystate}[0]{NJ}
\newcommand{\companyzip}[0]{07470}
%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{8in}{l@{\extracolsep{\fill}}r}
\textbf{\Large \myname}  & \myphone\\
\myaddress &  \myemail \\
\mycity, \mystate \ \myzip & \myurl\\
\end{tabular*}
\\

\vspace{0.75in}

\today

\recipient

\recipienttitle

\company

\companyaddress

\companycity, \companystate \ \companyzip


\vspace{0.3in}


\recipient:
\vspace{0.2in}

It was a pleasure meeting and speaking with you at FedEx this afternoon. You mentioned that an internship or other summer position with Bank of America was a possibility, and I'd like you to know that this would be the the chance of a lifetime for me. I have been programming since I was five years old, profiting from it since I was eleven, and would simply love the opportunity to put my skills to work in an office setting.

\vspace{0.15in}
My business experience has included and depended on work in social media and marketing. A large majority of my business comes from word-of-mouth referrals, thanks to lasting trust formed between myself and my clients. This trust is much like that which Bank of America seeks to build; an intimate relationship between bankers and account holders, without necessitating continuous physical contact.

\vspace{0.15in}
My ability to form lasting relationships, as well as my programming abilities, will prove to be a powerful asset to Bank of America. As my enclosed resume shows, I possess the technical abilities to complete complex problem-solving and programming tasks, and I have proven that I am capable of understanding what makes people want to work together for a long time. I welcome the opportunity to use my knowledge in such an environment that I can not only contribute, but learn from others with more work experience.

\vspace{0.15in}
I eagerly await your response. Please do not hesitate to contact me with any questions.

\vspace{0.15in}
\vspace{0.2in}
Sincerely,

\vspace{0.75in}
\myname

\myphone

\myemail

\end{document}